### 2014-09-14 notes.Rmd
app engine, writeup website

>>>>

## New product OR new service OR new business

Housing sale data, of interest to REITs, realtors, consumer housing market, individuals.

Product ideas:

* app for personal use. History of house sales in a given postcode, outlook for future growth, summary stats from other sources. Who'd use this? Eventually be bought out by Zoopla etc. for integration with their services. Do they offer this stuff already? 
  * Currently rightmove lists past house sales for an area
  * ONS offers clunky postcode datasets: http://www.neighbourhood.statistics.gov.uk/dissemination/LeadAreaSearch.do?a=7&i=1001&m=0&s=1410700363772&enc=1&areaSearchText=nw9+6ef&extendedList=false&searchAreas=
  * Crime statistics: http://www.crime-statistics.co.uk/postcode

Input postcode of interest, get nice visualisation of previous house sales, median rolling prices. Integrated with other data. Also offer surrouding postcode data for comparison.
